### 2021-05-17 writing/manuscript.Rmd
Fixed a couple small things, and confirmed that this knits fine

**Author Note.** A reproducible version of this manuscript, including all analysis and visualization code and data, is available at <https://github.com/themusiclab/form-function-kids>. Audio excerpts from the *Natural History of Song Discography* are available at <https://osf.io/vcybz> and can be explored interactively at <https://themusiclab.org/nhsplots>; all other study data and materials are available at <https://osf.io/b9tnu>. The study was preregistered at <https://osf.io/56zne>. For assistance, please contact C.H., L.C-T., and S.A.M.

@@

# format p-values automatically
format_p <- function(p) {
  if (p < .001) {
    return("< .001")
  } else {
    return(paste0("= ", round(p, digits = 3)))
  }
}

@@

f <- function(num) {
  round(num,2) %>% format(., nsmall=0,big.mark=",")
}

@@

# results from music feature analysis
load(here("results", "feature_analysis.RData")) # this is only temporarily included...
load(here("results", "selected_features.RData"))

@@

To measure the degree to which these inferences change through development, we fit a simple linear regression predicting children's average accuracy from age, finding a small but significant effect (*F*(1, `r mods$accuracy$age$df.residual %>% f`) = `r mods$accuracy$age$statistic %>% f`, *p* `r mods$accuracy$age$p.value %>% format_p()`, *R*^2^ `r mods$accuracy$age$r.squared %>% format_p()`), consistent with our exploratory analyses and preregistered hypothesis (i.e., a small, or practically non-significant increase in accuracy).

@@

In all cases, children's inferences were highly predictive of adults', with *R*^2^ values approaching 1 (Figure 3a-c; dance: *F*(1, `r mods$kfc_fc$dance$df.residual %>% f`) = `r mods$kfc_fc$dance$statistic %>% f`, *R*^2^ = `r mods$kfc_fc$dance$r.squared %>% f`; lullaby: *F*(1, `r mods$kfc_fc$lullaby$df.residual %>% f`) = `r mods$kfc_fc$lullaby$statistic %>% f`, *R*^2^ = `r mods$kfc_fc$lullaby$r.squared %>% f`; healing: *F*(1, `r mods$kfc_fc$healing$df.residual %>% f`) = `r mods$kfc_fc$healing$statistic %>% f`, *R*^2^ = `r mods$kfc_fc$healing$r.squared %>% f`; all *p* \<.001). This relationship was also robust when inferences were reduced from a continuous score to a discrete ranking of the songs by guessing percentage. We quantified the strength of this relationship using Kendall's rank correlation coefficient $\tau$: a more conservative, non-parametric measure of correlation. Again, there was a strong positive correlation between children's and adults' inferences for all song types (dance: $\tau$ = `r mods$tau$dance$estimate %>% round(3)`; lullaby: $\tau$ = `r mods$tau$lullaby$estimate %>% round(3)`; healing: $\tau$ = `r mods$tau$healing$estimate %>% round(3)`; all *p* \<.001).

>>>>

**Author Note.** A reproducible version of this manuscript, including all analysis and visualization code and data, is available at <https://github.com/themusiclab/form-function-kids>. Audio excerpts from the *Natural History of Song Discography* are available at <https://osf.io/vcybz> and can be explored interactively at <https://themusiclab.org/nhsplots>; all other study data and materials are available at <https://osf.io/b9tnu>. The study was preregistered at <https://osf.io/56zne>. For assistance, please contact C.B.H., L.C-T., and S.A.M.

@@

# format p-values automatically
format_p <- function(p) {
  if (p < .001) {
    return("< .001")
  } else if (p > .01) {
    return(paste0("= ", round(p, digits = 2)))
  } else {
    return(paste0("= ", round(p, digits = 3)))
  }
}

@@

f <- function(num) {
  round(num,2) %>% format(., nsmall=0, big.mark=",")
}

f2 <- function(num) {
  formatC(num, 2, format="f") %>% format(., nsmall=0, big.mark=",")
}

@@

# results from music feature analysis
load(here("results", "selected_features.RData"))

@@

To measure the degree to which these inferences change through development, we fit a simple linear regression predicting children's average accuracy from age, finding a small but significant effect (*F*(1, `r mods$accuracy$age$df.residual %>% f`) = `r mods$accuracy$age$statistic %>% f2`, *p* `r mods$accuracy$age$p.value %>% format_p()`, *R*^2^ `r mods$accuracy$age$r.squared %>% format_p()`), consistent with our exploratory analyses and preregistered hypothesis (i.e., a small, or practically non-significant increase in accuracy).

@@

In all cases, children's inferences were highly predictive of adults', with *R*^2^ values approaching 1 (Figure 3a-c; dance: *F*(1, `r mods$kfc_fc$dance$df.residual %>% f`) = `r mods$kfc_fc$dance$statistic %>% f`, *R*^2^ = `r mods$kfc_fc$dance$r.squared %>% f`; lullaby: *F*(1, `r mods$kfc_fc$lullaby$df.residual %>% f`) = `r mods$kfc_fc$lullaby$statistic %>% f`, *R*^2^ = `r mods$kfc_fc$lullaby$r.squared %>% f`; healing: *F*(1, `r mods$kfc_fc$healing$df.residual %>% f`) = `r mods$kfc_fc$healing$statistic %>% f`, *R*^2^ = `r mods$kfc_fc$healing$r.squared %>% f`; all *p* \<.001). This relationship was also robust when inferences were reduced from a continuous score to a discrete ranking of the songs by guessing percentage. We quantified the strength of this relationship using Kendall's rank correlation coefficient $\tau$: a more conservative, non-parametric measure of correlation. Again, there was a strong positive correlation between children's and adults' inferences for all song types (dance: $\tau$ = `r mods$tau$dance$estimate %>% round(3)`; lullaby: $\tau$ = `r mods$tau$lullaby$estimate %>% round(3)`; healing: $\tau$ = `r mods$tau$healing$estimate %>% round(3)`; all *p* \< .001).
